Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-18 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: maselli coeff. added to table up to j = 1, upd table caption

\begin{table}[t]
\begin{tabular}{c | c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
\hline
EdGB        & 4 & 0.0107    & 0.0044    & $-$0.2480 & $-$1.101 &  \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
dCS         & 4 & 3.1964    & 6.3619    & 41.199    & 794.66   &  \cite{Wagle:2021tam}  \\
cubic EFT   & 4 & $-$0.5813 & 2.6469    & $-$3.8620 & 265.12   & \cite{Cano:2021myl} \\
quartic EFT & 6 & $-$0.2114 & $-$0.6070 & $-$1.5263 & 171.35   & \cite{Cano:2021myl}  \\
\hline
\hline
\end{tabular}
\caption{Summary of theory-specific QNM calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
references from which we used the results from.\agcomm{Just leaving this comment
as a reminder to expand this table to include the GR values from Maselli et al.}
}
\label{tab:ref_theories_qnms}
\end{table}

@@

\agcomm{Have not gone through the appendices, because there might be sections that still
need to be completed.}

@@

>>>>

\begin{table*}[t]
\begin{tabular}{c | c c c c c c c c c c}
\hline
\hline
Theory      & $\omega^{(0)}_{220}$ & $\tau^{(0)}_{220}$ & $\omega^{(1)}_{220}$ & $\tau^{(1)}_{220}$ & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & Ref.  \\
\hline
GR          & 0.3737               & 11.2407            &  0.1258              & 0.2522             & --  & --                          & --                        & --                          & --                        & \cite{Maselli:2019mjd} \\
\hline
EdGB        & --                   & --                 &  --                  &                    & 4   & 0.0107                      & 0.0044                    & $-$0.2480                   & $-$1.101                  & \cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} \\
dCS         & --                   & --                 &  --                  &                    & 4   & 3.1964                      & 6.3619                    & 41.199                      & 794.66                    & \cite{Wagle:2021tam}  \\
cubic EFT   & --                   & --                 &  --                  &                    & 4   & $-$0.5813                   & 2.6469                    & $-$3.8620                   & 265.12                    & \cite{Cano:2021myl} \\
quartic EFT & --                   & --                 &  --                  &                    & 6   & $-$0.2114                   & $-$0.6070                 & $-$1.5263                   & 171.35                    & \cite{Cano:2021myl}  \\
\hline
\hline
\end{tabular}
\caption{Summary of theory-specific QNM calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(n)}_{220}$ and decay time $\delta \tau^{(n)}_{220}$, and the
references from which we used the results from.
%
We also included for comparison the GR coefficients, up to $j=1$, obtained in Ref.~\cite{Maselli:2019mjd}.
%
The remaining GR coefficients for $1< j \leqslant 4$, for which their non-GR counterpart cannot be determined as of yet for
the theories under consideration, can be found in Table~I of Ref.~\cite{Maselli:2019mjd}.
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

% \agcomm{Have not gone through the appendices, because there might be sections that still
% need to be completed.}

In this Appendix, we show how we fixed the coefficients in the ParSpec using
QNM calculations found in the literature for the theories described in
Sec.~\ref{sec:review_theories}.

@@

We start by considering EdGB gravity, for which the QNMs of nonrotating and
slowly-rotating BHs where calculated in
Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn} and~\cite{Pierini:2021jxd},
respectively.
